\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-05-31 nips2015.tex
ENH: more

Consider the following algorithm
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

Thus the iterates $(y^{(k)},p^{(k)},x^{(k)},q^{(k)})$ generated by
Algorithm \ref{Tab:algo} converge ergodically to a
$(\rho,\epsilon)$-Nash Equilibrium for the GSP \eqref{eq:unconstrained_pb}
in no more than $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ steps.
\end{theorem}

>>>>

Consider the following algorithm
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$
\Ensure $(\rho, \epsilon)$-Nash equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
Equilibrium for the GSP \eqref{eq:unconstrained_pb}
in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
\end{theorem}
